# ST 512 HW 2 - Savannah Harrison

## #1

```{r}
lima <- read.table("lima.txt", header = TRUE)
```

```{r}
lima_model <- lm(ascorbic ~ cultivar + pct.dry, data = lima)
summary(lima_model)
```

a\) **standard deviation of the residual errors =** **8.186**

b\) **C - Minimally plausible**

c\) **p-value: 8.303e-06, test statistic: 1.49e-06**

d\) **From the anova table, we would reject the null and conclude there is a difference between the ascorbic acid of plants from different cultivars when comparing plants with the same percent dry matter.**
**F statistic: 6.3742, p-value: 0.0145**

    ```{r}
    anova(lima_model)
    ```
    e\)

```{r}
#Creating plot of the residuals vs. the fitted values
residualplot <- plot(x = fitted(lima_model), y = resid(lima_model), xlab = "Fitted values", ylab = "Residuals")
abline(h = 0, lty = "dashed", col = "blue")
```

```{r}
#created Q-Q plot
QQplot <- qqnorm(y = resid(lima_model))
          qqline(y = resid(lima_model), col = "blue")
```

f)  **While it seems like there may be some small spread in the residual plot, it is not large enough to violate the constant error variance assumption. For the Q-Q plot, it looks like the ends might be drifting away from the line, but just like the residual plot, this discrepency is not large enough to violate the normality assumption.**

## #2

a)  **(0.101,0.185)**

```{r}
#Estimate +- (SE)(Critical Value) df = 21
.143+(.020*2.0796)
.143-(.020*2.0796)
```

b)  

    (i) **YES**
    (ii) **NO**

## #3

a)  When comparing two cereals with the same fat content, fiber content, and manufacturer, a cereal with 5 grams of sugar per serving will have a nutritional rating that is **3.58 smaller** than a cereal with 3 grams of sugar per serving, on average.

    ```{r}
    -1.79*2
    ```

b)  When comparing two cereals with the same fat content, fiber content, and sugar content, a cereal manufactured by Quaker (Q) will have a nutritional rating that is **4.44 larger** than a cereal manufactured by General Mills (GM).

## #4

**29.14** 

fat = 0 fiber = 1.0 sugars = 14

```{r}
50.23 + (-3.57*0) + (2.9*1.0) + (-1.79*14) + (1.07*1)
```

## #5

**4.06**

```{r}
#observed - predicted
33.2 - 29.14
```

## #6

**20.139**

```{r}
#(SS(Model)/df) / (SS(Error)/df)
(1270/3)/(1030/49)
```
